Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-27 methods-and-results.Rmd
:bug: fromula render

\subsubsection{Sample}
The original studies included `r sum(missS123$pptFull)` participants ($N_{S1}=$`r missS123$pptFull[missS123$study==1]`, $N_{S2}=$`r missS123$pptFull[missS123$study==2]`, $N_{S3}=$`r missS123$pptFull[missS123$study==3]`) with a total `r format(sum(missS123$nFull), big.mark=",")` measurements. The studies differed substantially in the maximum length of participation ($N_{t:S1}=$`r missS123$timeFull[missS123$study==1]`, $N_{t:S2}=$`r missS123$timeFull[missS123$study==2]`, $N_{t:S3}=$`r missS123$timeFull[missS123$study==3]`).

>>>>

\subsubsection{Sample}
The original studies included `r sum(missS123$pptFull)` participants ($N_{S1}=$ `r missS123$pptFull[missS123$study==1]`, $N_{S2}=$ `r missS123$pptFull[missS123$study==2]`, $N_{S3}=$ `r missS123$pptFull[missS123$study==3]`) with a total of `r format(sum(missS123$nFull), big.mark=",")` measurements. The studies differed substantially in the maximum length of participation ($N_{t:S1}=$`r missS123$timeFull[missS123$study==1]`, $N_{t:S2}=$ `r missS123$timeFull[missS123$study==2]`, $N_{t:S3}=$ `r missS123$timeFull[missS123$study==3]`).
